Case study: Analysis on smart meter data

### 2019-08-25 smart_meter.Rmd
smart meter analysis added

```{r cust3_hd_dw, fig.cap="Violin plots of hourly consumption across different day of the week for the second household."}
data_sm3 %>% granplot("day_week", "hour_day", "general_supply_kwh", plot_type = "violin") + ggtitle("Violin plot of energy consumption across hour-of-day and day-of-week for Household 2") + scale_x_discrete(breaks = seq(0,23,3))
```

@@

```{r cust1_dw_my,fig.cap="this is a caption"}
library(ggplot2)

data_sm1 %>% granplot("month_year", "day_week", response = "general_supply_kwh", plot_type = "lv", quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9)) +  ggtitle("LV plot of energy consumption across days of week by month of years for Household 1")+ scale_y_continuous(breaks = seq(0, 1.5, 0.25))
```

```{r cust3_dw_my, fig.cap="this is a caption"}
library(ggplot2)

data_sm3 %>% granplot("month_year", "day_week", response = "general_supply_kwh", plot_type = "lv") +  ggtitle("LV plot of energy consumption across days of week by month of years for Household 3")+ scale_y_continuous(breaks = seq(0, 1.5, 0.25))
```

>>>>

```{r cust3_hd_dw, fig.cap="Violin plots of hourly consumption across different day of the week for the second household. Hours before 10am and after 10pm have a bulge implying those hours are pretty consistent. Hours in between these have a long right tail which are even higher for weekends."}
data_sm3 %>% granplot("day_week", "hour_day", "general_supply_kwh", plot_type = "violin") + ggtitle("Violin plot of energy consumption across hour-of-day and day-of-week for Household 2") + scale_x_discrete(breaks = seq(0,23,3))
```

@@

```{r cust1_my_dw, fig.cap="Letter value plots of energy consumption across days of the week and months for the first household. Letter value plots convey detailed information about tails of the distribution and outliers are unexpected observations rather than extreme observations. M, F, E, D and C represents 50%, 25%, 12.5%, 6.25% and 3.13% of the tail area respectively.Outliers are colored in red. It can be noted that they do not typically consume more than 0.25 KwH in the weekdays. Their tail behaviors are not so distinctly visible because of the consistency in their behavior."}

library(ggplot2)

data_sm1 %>% granplot("month_year", "day_week", response = "general_supply_kwh", plot_type = "lv") +  ggtitle("LV plot of energy consumption across days-week by month-year for Household 1")+ scale_y_continuous(breaks = seq(0, 1.5, 0.25))

```

```{r cust3_my_dw, fig.cap="Letter value plots of energy consumption across days of the week and months for the first household. Contrary to the first household, outliers appear at an energy usage beyond 0.75 KwH. The extreme values in the tail of the distribution are represented by different letter values. In March, once can observe the F letter value to range between 0.75 to 1.25 KwH on weekends and between 0.25 to 0.75 KwH on weekdays (represented by letter value D), which is far more higher than subsequent months and comparable to summer month December. For unusual days or more volatile days of the week, one can expect to see more distinct letter values.This reinforces the fact that their behavior changes across months but not so much between days of the week."}

library(ggplot2)

data_sm3 %>% granplot("month_year", "day_week", response = "general_supply_kwh", plot_type = "lv") +  ggtitle("LV plot of energy consumption across days of week by month of years for Household 2")+ scale_y_continuous(breaks = seq(0, 1.5, 0.25))
```
